### 2019-09-12 2019_neurips_vigil/intro.tex
added some additional references to intro

, and now withhigh-performing neural systems that can answer short ques-tions provided they are given a text that contains the answer(e.g., Seo et al., 2016; Wang et al., 2018).

@@

@@

>>>>

, and now with high-performing neural systems that can answer short ques-tions provided they are given a text that contains the answer e.g.~\cite{wang2018glue}

@@

\cite{levesque2012winograd}

@@

bAbI~\cite{weston2015towards}
